The fundamental geometry of dynamic experiences is preserved in memory

### 2018-06-22 main.tex
checking in progress

% \begin{figure}[t!]
% \centering
% \includegraphics[width=1\textwidth]{figs/1_video_recall_models.pdf}
% \caption{\label{fig:model}Topic models for the video and verbal recall. A. A timepoints (1976) by topics (100) matrix was created by fitting a topic model to overlapping segments of the moment-by-moment video text descriptions.  Each row represents the most likely mixture of topics for a given timepoint. Each columns represents a different topic. The darker the color, the higher the probability that the topic is contained in that timepoint. B. A timepoints (1976) by topics (100) matrix representing group average topic model of the recall transcripts.  All participant's recall transcripts were transformed using the topic model fit to the video descriptions and then resampled to the same length (1976). C. A viewing-time (1976) by recall-time (1976) correlation matrix representing the correlation of each moment of the video model with every moment of the average recall model. The darker the color, the higher the correlation between the video and recall models at a given timepoint. D. A 3D embedding of the video and recall topic models reduced using spectral embedding. }
% \end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=.75\textwidth]{figs/2_eventseg.pdf}
\caption{\label{fig:eventseg} Event segmentation analysis of the video and recall models. A. A recall-time (294) by topics (100) matrix representing a recall model for a single participant (participant \#13).  B. A recall-time (294) by recall-time (294) correlation matrix for participant \#13. The white squares along the diagonal outline events, i.e. neighboring timepoints with a stable and similar topic vector. C. An events (34) by topics (100) matrix where each row represents the average topic vector for each event in the video model.  D. An events (27) by topics (100) matrix where each row represents the average topic vector for each event in the recall model. E. A recall events (27) by video events (34) correlation matrix representing the `match' between each video and recall event. The black squares identify the video event with the highest correlation to a given recall event. F. A group averaged recall events (34) by video events (34) correlation matrix.  The black squares identify the video event with the highest correlation to a given average recall event. G. 2D embeddings (reduced with UMAP algorithm) of each participants' recall event model (example shown in D). Each dot represents a recall event and the connecting lines indicate the order of recall. Colors indicate the most likely video event that the participant was describing as determined by the video-recall matching model.  H. 2D embedding of video and average recall event models.}
\end{figure}

Next, we explored the idea that the individual `blocks' along the diagonals of the recall matrices represent the recall of a particular video event. To test this, first we created a video event model, which was done by averaging together neighboring topic vectors that the were classified to be in the same event (\ref{fig:eventseg}c), resulting in an events (34) by topics (100) matrix.  We performed the same procedure for the recall matrices (see \ref{fig:eventseg}d for example). Then, we computed the correlation between these two event models, resulting in a video events (34) by recall events (8-27, depending on the participant) correlation matrix (see \ref{fig:eventseg}e). These matrices represent the extent to which each recall event is similar to each video event (for each participant). To determine which video events the recall events most likely referred to, for each recall event, we found the index of the video event with the highest correlation (i.e. the argmax).  This is depicted in \ref{fig:eventseg}e as the cell highlighted with the black box for each column in the video-recall event correlation matrix. Notably, our algorithm suggests that the example participant recalled the events largely in order (occasionally skipping over an event).

@@

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=1\textwidth]{figs/4_behav_eventseg.pdf}
\caption{\label{fig:behav}Naturalistic extensions of classic memory analyses. A-C use the `smooth' approach and D-F use the `best' approach (see Methods for details). A/D. The probability of first recall as a function of the serial position the the event during encoding. B/E. Given recall of event i, the probability that the next recalled item will be from serial position i \rpm~lag. C/F. Proportion recalled as a function of serial position. All error bars are the standard error of the mean derived from a bootstrap resampling procedure.
}
\end{figure}

>>>>

\begin{figure}[ht!]
\centering
\includegraphics[width=\textwidth]{figs/2_eventseg_v4.pdf}
\caption{\label{fig:eventseg} Event segmentation analysis of the video and recall models. For all plots, darker colors indicate greater values and the range of each plot is 0-1.  A). A timepoints (1976) by topics (100) matrix representing the video stimulus.  Each row represents the most likely mixture of topics for a given timepoint. Each columns represents a different topic. B). A timepoints (1976) by topics (100) matrix representing participant \#13's recall. C). A viewing-time (1976) by viewing-time (1976) correlation matrix representing the correlation of each moment of the video model with every other moment of the video model. The white boxes represent `events' recovered by a hidden Markov model. D). A recall-time (294 sentences) by recall-time (294) correlation matrix for participant \#13. E). An events (34) by topics (100) matrix where each row represents the average topic vector for each event in the video model.  F). An events (27) by topics (100) matrix where each row represents the average topic vector for each event in participant \#13's recall model. G. A recall events (27) by video events (34) correlation matrix for participant \#13. The yellow squares identify the video event with the highest correlation to a given recall event. F. A group averaged recall events (34) by video events (34) correlation matrix.  The yellow squares identify the video event with the highest correlation to a given average recall event.}
\end{figure}

@@

Next, we hypothesized that the individual `blocks' along the diagonals of the recall matrices represent the recall of a particular video event. To test this, first we created a video event model, which was done by averaging together neighboring topic vectors that the were classified to be in the same event (\ref{fig:eventseg}c), resulting in an events (34) by topics (100) matrix.  We performed the same procedure for the recall matrices (see \ref{fig:eventseg}d for example). Then, we computed the correlation between these two event models, resulting in a video events (34) by recall events (8-27, depending on the participant) correlation matrix (see \ref{fig:eventseg}e). These matrices represent the extent to which each recall event is similar to each video event (for each participant). To determine which video events the recall events most likely referred to, for each recall event, we found the index of the video event with the highest correlation (i.e. the argmax).  This is depicted in \ref{fig:eventseg}e as the cell highlighted with the black box for each column in the video-recall event correlation matrix. Notably, our algorithm suggests that the example participant recalled the events largely in order (occasionally skipping over an event).

@@

\begin{figure}[t!]
\centering
\includegraphics[width=1\textwidth]{figs/4_behav_eventseg.pdf}
\caption{\label{fig:behav}Naturalistic extensions of classic memory analyses. A-C use the `smooth' approach and D-F use the `best' approach (see Methods for details). A/D. The probability of first recall as a function of the serial position the the event during encoding. B/E. Given recall of event i, the probability that the next recalled item will be from serial position i \rpm~lag. C/F. Proportion recalled as a function of serial position. All error bars are the standard error of the mean derived from a bootstrap resampling procedure.
}
\end{figure}

@@
